An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-03-27 Article/EconGrowth2.Rnw
Added definition of spaghettiGraphLevel to the EconGrowth2.Rnw file.
Removed #' @export from spaghettiGraphLevel.

>>>>

<<constants, include=FALSE>>=
# Graph Heights
# #' @export
maxHeight <- 8.5 # Inches
# #' @export
ninePanelScatterGraphHeight <- maxHeight # Inches
# #' @export
# ninePanelTernaryGraphHeight <- 7 # Inches
# #' @export
# ninePanelSpaghettiGraphHeight <- 7 # Inches

# Graph Widths
# #' @export
maxWidth <- 6.5 # Inches
# #' @export
fourPanelScatterGraphWidth <- maxWidth # Inches
# #' @export
# threePanelScatterGraphWidth <- maxWidth*0.75 # Inches
# #' @export
# onePanelScatterGraphWidth <- maxWidth*0.25
# #' @export
# fourPanelTernaryGraphWidth <- maxWidth
# #' @export
# twoPanelTernaryGraphWidth <- maxWidth*0.45
# #' @export
# fourPanelSpaghettiGraphWidth <- maxWidth
# #' @export
# twoPanelSpaghettiGraphWidth <- maxWidth*0.55
# #' @export
# onePanelSpaghettiGraphWidth <- maxWidth*0.4

#' @export
presentationGraph1RowHeight <- 2.8 # Inches
#' @export
presentationGraph2ColWidth <- 2 # Inches
#' @export
presentationGraph1ColWidth <- 2*presentationGraph2ColWidth
# #' @export
# keyTextSize <- 0.85 # 85% of normal size
# #' @export
# keyColumns <- 1 # Want only 1 column in the key for lattice graphs
# #' @export
# defaultKeyXLoc <- 0.01 # x position of the key. This default is good for 9-panel graphs.
# #' @export
# defaultKeyYLoc <- 0.95 # y position of the key. This default is good for 9-panel graphs.
# Parameter graphs are tricky to ensure same size. I've found that with height set to 5 in for the 
# cd graphs and 2.93 in for the sf graphs, I get a nearly-exact match with graph size. From these settings I 
# can set up 2 equations:
#    5 in = 2*hgraph + haxis
#    2.93 in = hgraph + haxis
# to estimate that h_axis = 0.86 in and hgraph = 2.05 in.
# #' @export
h_param_graph <- 2.07 # Inches for a single panel
# #' @export
h_param_axis <- 0.86 # Inches (also includes whatever margin is applied)
# #' @export
# sfParameterGraphHeight <- h_param_graph + h_param_axis
# #' @export
cdParameterGraphHeight <- 2*h_param_graph + h_param_axis
# #' @export
cesParameterGraphHeight <- 3*h_param_graph + h_param_axis
# #' @export
linexParameterGraphHeight <- h_param_graph + h_param_axis
# #' @export
sfParameterGraphWidth <- maxWidth
# #' @export
cdParameterGraphWidth <- maxWidth
# #' @export
# cdTernaryGraphWidth <- maxWidth/2.2
# #' @export
# cdSpaghettiGraphWidth <- maxWidth/2.2
# #' @export
cesParameterGraphWidth <- maxWidth
# #' @export
linexParameterGraphWidth <- maxWidth
# Other graph parameters that apply to all graphs
# #' @export
scaleTextSize <- 0.8  # Multiple of normal size
# #' @export
scaleTickSize <- -0.5 # 50% of normal size and pointing INWARD!

spaghettiGraphLevel <- 0.95 # Spaghetti graph bands will encompass 95% of the data.
@

% These equations are used in several locations in the paper.
% By defining commands for them, we ensure consistent appearance
% of the equations when they are used.
